---
title: "Mapping animals social landscape helps tracking fine-scale disease spread in gregarious species"
author: "Kevin Morelle^1,2^*, Second Author^3^"
output:
  bookdown::word_document2:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    df_print: kable
    keep_md: yes
    number_sections: no
    toc: no
    reference_docx: Word_template.docx
  word_document:
    toc: no
bibliography:
- Contact.bib
- knitcitations.bib
csl: ecology.csl
---

^1^ Max Planck Institute of Animal Behavior (MPIAB), Radolfzell, Germany

^2^ University of Life Sciences (CULS), Prague, Czech Republic

^3^ Blabla


`*` Corresponding author: kmorelle@ab.mpg.de


# ABSTRACT

Animal social behaviour is under focus since some decades. Integrating approach merging different field, like movement ecology, disease ecology and socio-biology are emerging over the last years. Yet, there is still a gap in linking those approach within the landscape ecology field. Movement data are generally use for individuals or population level investigations, resource selection, habitat use, movement strategies. Yet these doesn't inform us about social whereabouts, e.g animals moving or spending time together. Areas, patches or grids used by multiple animals simultaneously or with some short time lag are key for information and diseases transfer in animal populations. using a simple grid-based tool, we converted available animal tracking data into social landscapes. This tool uses a set of metrics enabling to uncover the relative importance of landscape for direct and indirect social interactions. Specifically it enables to visualize social hubs where information or diseases can be transmitted within individuals. We apply this approach to a large dataset of GPS-tracked wild boar across Europe to make inference about landscape properties driving social interactions within this species carying concern in terms of disease transmission _+cheetah data from IZW?_, and illustrate how the proposed approach can potentially fill a missing gap in the movement-social and landscape scientific bubble. 


*Keywords*: Social hubs, interactions, aggregations, disease ecology, information, wild boar




```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library("knitr")

### Chunk options: see http://yihui.name/knitr/options/ ###
## Text results
opts_chunk$set(echo = FALSE, warning = TRUE, message = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)

## Cache
# opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
opts_chunk$set(fig.path = "output/figures/")

```


```{r knitcitations, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```



# INTRODUCTION


# OBJECTIVE - RESEARCH QUESTIONS


# METHODS

## Data preparation

We used the Euroboar platform, which contains the largest European wild boar GPS tracking dataset (www.euroboar.org). Euroboar is part of the umbrella Eurommals initiative which aims at...
The database contains *xxx* individuals GPS tracks across Europe. These data presents a wide variations in terms of sampling effort (i.e. number of locations per unit of time) and period (duration of tracking). For the present study we focus our investigations on those study areas in which multiple animals were simultaneously tracked. We extracted days in which 4 or more individuals were tracked and we resampled the tracks to one location every hours. Our final dataset comprises *xx* study areas, *xx* individuals and *xxxxx* locations.
We considered as a *direct interactions* any simultaneous relocations between minimum two individuals within 10 minutes interval and maximum 50 meters apart distance. An *indirect interactions* was defined as the consecutive (in time) use of the same grid cell by one or more individuals. To assess whether an interaction took place between individuals of the same group (*within-group interaction*) or between individuals belonging to different groups (*between-groups interaction*), we computed a set of interactions patterns metrics at the dyadic level. Specifically, we calculated the following metrics: *homerange overlap*,*proximity index*, *coefficient of sociality*, *Half-weight association index* and *Correlation coefficient*. We classified dyads as belonging to the same group when **...**.

## Social interactions mapping

Application of a grid over your tracking data. Definition of a resolution. The decision on the resolution relies upon your species specific system and at which scale your are interested to observed interaction. Compromised between data resolution, species a priori knowledge of the social behaviour and scale of interest. To map social interaction over the landscape, we firstly deploy a grid over the tracking data. The grid resolution is a user-based parameter, which should be define according to the species of interest biological and ecological needs as well as to the research question. Within each of these grid we secondly calculated a set of metrics accounting for individuals / group of individuals direct and indirect interactions. The aim here is to elicit the relative value of the different landscape component (i.e. grid) in terms of social interactions (table *xxx*). As indirect metrics, we used the overal number of individuals having been observed in a grid cell , the frequency of grid visit and **...**. As direct metrics, we used the maximal and the mean number of simultaneously observed individuals, the duration of stay/visit in a grid and the mean inter-individuals distance. Within this calculation, we integrated the information on dyadic association (as described above) so that we could append to the observed (direct and indirect) interactions the level at which it took place, i.e. within or between groups.

```{r tbl_metrics, echo=FALSE}
Type <- c('indirect',
          'indirect',
          'indirect',
          'direct',
          'direct',
          'direct')
Metrics <- c('n_ind',
             'revisit_interval',
             'visit_frequency',
             'n_ind_max',
             'visit_duration',
             'group_composition')
Unit <- c('% of tracked individuals',
          'every x hours',
          'x by day/week/month',
          '% of tracked individuals',
          'hours',
          'index 0-1, 1 = always same individuals/dyads/group, 0=always different')
Description <- c('total number of distinct individuals having visited a grid over a particular time frame',
                 'max number of individual simulatenously observed in a grid',
                 '',
                 '',
                 '',
                 '')

tbl_metrics <- data.frame(Type, Metrics, Unit, Description)
library(flextable)

ft_metrics <- flextable(tbl_metrics)
ft_metrics <- merge_v(ft_metrics, j = "Type")
ft_metrics
```
We thirdly check for collinearity among our calculated metrics. We observed that **...**. 







## Steps 2: calculation of the metric at the grid level

## Steps 3: collinearity analysis

## Step 4: Modeling

### Generating pseudo-absences

[@barbet-massin2012] *We used four different methods to generate the pseudo-absences (using the biomod package in R, Thuiller et al. 2009): (i) random selection from all points within the studied area excluding available presence points (‘random’), (ii) random selection of points from all points outside of the suitable area estimated by a rectilinear surface envelope from the presence sample (surface range envelope model using only presence-only data, Thuiller et al. 2009; hereafter, the ‘SRE’ method), (iii) random selection of any point located at least one degree in latitude or longitude from any presence point (the ‘1°far’ method) and (iv) random selection of any available point located at least two degrees away from any presence point (the ‘2°far’ method). Note that pseudo-absences can be presences that were not retained within the presence sample used to build the models (i.e. false absences).*

We used an inferential and a extrapolation approach to decipher the environmetal drivers of wild boar interaction. In both approach, we used spatial regression with random forest   a machine learning (ML) approach which are know for their ability to consider spatial autocorrelation in datasets [@Sabatinez2015]

### Covariates

We used the following high resolution and open source layers from the European Copernicus observation system [@Re3data2014]: forest, grassland, water and wetness (resolution of 20m), the European settlement map (resolution of 2.5m) as well as the Corine landcover data (resolution of 100m). For river network, we used the Global River Network dataset [@Schneider2017]. For linear infrastructures (roads), we used OpenStreetmap using Geofabrik [@Ramm2017] and the osmdata R package [@Padgham2017] for relevant data extraction (see ESM 2 for detailed description of covariates). We scaled all data sources to a final resolution of 20m to investigate the process of habitat selection by dying wild boar. Covariate transformation was performed using the raster R package [@Hijmans2017a].

```{r tbl.var, echo=FALSE, fig.cap = tab.1_cap}

variable <- c('Landcover','Forest type','Tree cover density','Distance to forests',
              'Distance to croplands', 'Distance to grasslands',
              'Distance to settlements', 'Distance to roads',
              'Distance to paths', 'slope', 'aspect', 'roughness',
              'TPI','TRI', 'TWI' ,'Wetness', 'Distance to water', 'Distance to river')
type <- c('factor', 'factor','continuous','continuous','continuous','continuous',
          'continuous','continuous','continuous','continuous','continuous',
          'continuous','continuous','continuous','continuous', 'continuous', 'continuous', 'continuous')
resolution <- c('100 m','20 m','20 m','20 m','20 m','20 m','2.5 m','20 m','25 m',
                '25 m','25 m','25 m','25 m','25 m','25 m', '20 m', '20 m', '500 m')
description <- c('land cover classes as assigned by CORINE',
                 'dominant leaf type (broadleaved/coniferous) in area of minimum 0.5 ha surface and  10% tree cover density','level of tree cover density in a range from 0-100%', 'Distance in meters to forest edge',
                 'Distance in meters to agricultural crop edge. Agricultural areas including all arable lands. Do not include pasture and grasslands.', 
                 'Distance in meters to grassland edge',
                 'Distance in meters to settlement area edge. Settlement comes from raster dataset mapping human settlements in Europe based on SPOT5 and SPOT6 satellite imagery',
                 'Distance in meters to car/asphalted road',
                 'Distance in meters to walkable path/restricted to tractor',
                 'Rate of maximum change in elevation from each cell. Product derived from digital elevation model','Downslope direction of the maximum rate of change in value from each cell to its neighbors. Product derived from digital elevation model', 'Difference between the maximum and the minimum elevation of a cell and its 8 surrounding cells. Product derived from digital elevation model','Topographic Position Index calculated as the difference in elevation between a cell and the mean value of its 8 surrounding cells. Product derived from digital elevation model','Terrain Ruggedness Index, calculated as the mean of the absolute differences between the elevation of a cell and the value of its 8 surrounding cells. Product derived from digital elevation model','Topographic Wetness Index. Based on the calculation of the upslope contributing area. Higher TWI values indicate drainage depressions, lower values indicate crests and ridges. Product derived from digital elevation model', 
                'Probability of occurrence of water, indicating the degree of wetness',
                 'Distance in meters to any water features of type permanent water, temporary water, permanent wetness and temporary wetness as defined by Copernicus by-product',
                'Distance in meters to river stream')
source <- c('CORINE', 'COPERNICUS','COPERNICUS','COPERNICUS','CORINE','COPERNICUS','COPERNICUS',
            'OPENSTREETMAP','OPENSTREETMAP','COPERNICUS','COPERNICUS, EU-DEM','COPERNICUS, EU-DEM',
            'COPERNICUS, EU-DEM','COPERNICUS, EU-DEM','COPERNICUS, EU-DEM','COPERNICUS','COPERNICUS',
           'Global River Network' )
tbl.var <- data.frame(variable,description, type, resolution, source)
library(knitr)
kable(tbl.var)
```

[@ploton2020] [@lerest2014]

From [@Meyer2018]
*Random forest algorithm Random Forest bases on the concept of regression and classification trees, i.e. a series of nested decision rules for the predictors that determine the response. It repeatedly builds trees from random samples of the training data with each tree is a separate model of the ensemble. The estimations of all trees are finally averaged to produce the final estimate (Breiman, 2001). To overcome correlation between trees, only a subset of predictors (mtry) is randomly selected at each split. The best predictor from the random subset is used at the respective split to partition the data. mtry is considered as a hyperparameter that needs to be tuned for a respective dataset in order to obtain an optimal trade-off between under- and over-fitting of the data. For a further description of Random Forest, see Breiman, 2001, James et al., 2013 and Kuhn and Johnson (2013). In this study, the Random Forest implementation of the randomForest package (Liaw and Wiener, 2002) in R was applied and accessed via the caret package (Kuhn, 2016). Throughout the study, each Random Forest model consisted of 500 trees after no increase of performance could be observed using a higher number of trees. mtry was tuned for each value between two and the respective number of predictor variables.*

# APPLICATIONS



```{r Table-Iris}
kable(head(iris), caption = "A glimpse of the famous Iris dataset.")
```


```{r scatterplot, fig.cap="Just my first figure with a very fantastic caption."}
x <- rnorm(100)
y <- jitter(x, 1000)
plot(x, y)
```


# DISCUSSION

Discuss with other existing landscape-habitat available tools:

- Habitat network [@Peng2020]
- Grainscape toolbox
- Movescape [@BastilleRousseau2020]

Possible extension: multi-species, e.g. predator-prey interactions.

# CONCLUSIONS

Wrap up


# ACKNOWLEDGEMENTS

On the shoulders of giants.


# REFERENCES


###### Supplementary Table (on new page)

```{r Table-mtcars}
kable(mtcars[10:16, ], caption = "Now a subset of mtcars dataset.")
```


###### Supplementary Figure (on new page)

```{r Fig-landscape, fig.cap="A boxplot."}
a <- sort(rnorm(100))
b <- c(rep("Group Small", 35), rep("Group Big", 65))
boxplot(a ~ b)
```




```{r sessioninfo, eval = FALSE}
# set eval = FALSE if you don't want this info (useful for reproducibility) to appear 
sessionInfo()
# sessioninfo::session_info()
```
